---
title: "Portfolio1"
author: "Negar"
date: "4/09/2022"
output:
  pdf_document: default
  html_document: default
---

### Summary
This project is about topic modeling, which is an interesting task in NLP. In this project we are trying to identify major topics in unlabeled texts, and then see which words are essential for text that is labeled for topic.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(ggeasy)
library(formattable)
library(patchwork)
```

### Data Description
The independent variables of "StudentsPerformance.csv" are as follow:


| **Columns Name** | **Description** |  **Type**  |
|------------------|-----------------|------------|
| Gender | sex of students | character |
| Race/Ethnicity | ethnicity of students | character |
| Parental Level of Education | parents' final education | character |
| Lunch | having lunch before test (normal or abnormal) | character |
| Test Preparation Course | complete or not complete before test | character |
| Math Score | student math score out of 100 | integer |
| Reading Score | student reading score out of 100 | integer |
| Writing Score | student writing score out of 100 | integer |

**Note:** The dataset is free from any missing values.

```{r import dataset}
data = read.csv(here::here("Data","data","StudentsPerformance_renamed.csv"))
```

Firstly, let's figure out the performance of each field for males and females.

```{r first plot}
gender_performance <- data |> group_by(gender) |> summarise(
  math = mean(math),
  reading = mean(reading),
  writing = mean(writing))

plt1 <- ggplot(gender_performance, aes(x=gender, y=math, fill=gender)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=formattable(math, digits = 2, format = "f")), vjust=1.6, color="white", size=3.5)+
  theme_minimal()+
  ylab("score")+
  ggtitle("Math")+
  ggeasy::easy_center_title() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())
ggsave(here::here("Output", "Figures", "gender_math.tiff"), plt1, height = 6, width = 6)


plt2 <- ggplot(gender_performance, aes(x=gender, y=reading, fill=gender)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=formattable(reading, digits = 2, format = "f")), vjust=1.6, color="white", size=3.5)+
  theme_minimal()+
  ylab("score")+
  ggtitle("Reading")+
  ggeasy::easy_center_title() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())
ggsave(here::here("Output", "Figures", "gender_reading.tiff"), plt2, height = 6, width = 6)


plt3 <- ggplot(gender_performance, aes(x=gender, y=writing, fill=gender)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=formattable(writing, digits = 2, format = "f")), vjust=1.6, color="white", size=3.5)+
  theme_minimal()+
  ylab("score")+
  ggtitle("Writing")+
  ggeasy::easy_center_title()
ggsave(here::here("Output", "Figures", "gender_writing.tiff"), plt3, height = 6, width = 6)

plt1 / plt2 / plt3 + plot_layout(guides='collect')
```

We can see that male has better performance on math field, but worse on reading and writing. Secondly, see the performance of ethnicity.

```{r second plot}
ethnicity_performance <- data |> group_by(ethnicity) |> summarise(
  math = mean(math),
  reading = mean(reading),
  writing = mean(writing))

plt1_1 <- ggplot(ethnicity_performance, aes(x=ethnicity, y=math, fill=ethnicity)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=formattable(math, digits = 2, format = "f")), vjust=1.6, color="white", size=3.5)+
  theme_minimal()+
  ylab("score")+
  ggtitle("Math")+
  ggeasy::easy_center_title() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())
ggsave(here::here("Output", "Figures", "ethnicity_math.tiff"), plt1_1, height = 6, width = 6)

plt2_2 <- ggplot(ethnicity_performance, aes(x=ethnicity, y=reading, fill=ethnicity)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=formattable(reading, digits = 2, format = "f")), vjust=1.6, color="white", size=3.5)+
  theme_minimal()+
  ylab("score")+
  ggtitle("Reading")+
  ggeasy::easy_center_title() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())
ggsave(here::here("Output", "Figures", "ethnicity_reading.tiff"), plt2_2, height = 6, width = 6)

plt3_3 <- ggplot(ethnicity_performance, aes(x=ethnicity, y=writing, fill=ethnicity)) +
  geom_bar(stat="identity")+
  geom_text(aes(label=formattable(writing, digits = 2, format = "f")), vjust=1.6, color="white", size=3.5)+
  theme_minimal()+
  ylab("score")+
  ggtitle("Writing")+
  ggeasy::easy_center_title()
ggsave(here::here("Output", "Figures", "ethnicity_writing.tiff"), plt3_3, height = 6, width = 6)

plt1_1 / plt2_2 / plt3_3 + plot_layout(guides='collect')
```

Group E, obviously, has best performance for all the fields, and group A is the worst. Then, let's see the result of score and test preparation.

```{r third plot}
plt1_1_1 <- ggplot(data) +
  aes(x = pre,
      y = math,
      fill = pre,
      color = pre) +
  geom_jitter(height = 0,
              width = .4) +
  geom_boxplot(color = "black",
               alpha = .5)+
  xlab("preparation")+
  ggtitle("Math vs. Preparation Test")+
  ggeasy::easy_center_title() 
ggsave(here::here("Output", "Figures", "preparation_math.tiff"), plt1_1_1, height = 6, width = 6)
plt1_1_1

plt2_2_2 <- ggplot(data) +
  aes(x = pre,
      y = reading,
      fill = pre,
      color = pre) +
  geom_jitter(height = 0,
              width = .4) +
  geom_boxplot(color = "black",
               alpha = .5)+
  xlab("preparation")+
  ggtitle("Reading vs. Preparation Test")+
  ggeasy::easy_center_title()
ggsave(here::here("Output", "Figures", "preparation_reading.tiff"), plt2_2_2, height = 6, width = 6)
plt2_2_2

plt3_3_3 <- ggplot(data) +
  aes(x = pre,
      y = writing,
      fill = pre,
      color = pre) +
  geom_jitter(height = 0,
              width = .4) +
  geom_boxplot(color = "black",
               alpha = .5)+
  xlab("preparation")+
  ggtitle("Writing vs. Preparation Test")+
  ggeasy::easy_center_title()
ggsave(here::here("Output", "Figures", "preparation_writing.tiff"), plt3_3_3, height = 6, width = 6)
plt3_3_3
```

The score distribution got narrower if students complete the preparation before test, and also we can see that the average of the score is better.

```{r forth plot}
plt1_1_1_1 <- ggplot(data) +
  aes(x = lunch,
      y = math,
      fill = lunch,
      color = lunch) +
  geom_jitter(height = 0,
              width = .4) +
  geom_boxplot(color = "black",
               alpha = .5)+
  ggtitle("Math vs. Lunch")+
  ggeasy::easy_center_title()
ggsave(here::here("Output", "Figures", "lunch_math.tiff"), plt1_1_1_1, height = 6, width = 6)
plt1_1_1_1

plt2_2_2_2 <- ggplot(data) +
  aes(x = lunch,
      y = reading,
      fill = lunch,
      color = lunch) +
  geom_jitter(height = 0,
              width = .4) +
  geom_boxplot(color = "black",
               alpha = .5)+
  ggtitle("Reading vs. Lunch")+
  ggeasy::easy_center_title()
ggsave(here::here("Output", "Figures", "lunch_reading.tiff"), plt2_2_2_2, height = 6, width = 6)
plt2_2_2_2

plt3_3_3_3 <- ggplot(data) +
  aes(x = lunch,
      y = writing,
      fill = lunch,
      color = lunch) +
  geom_jitter(height = 0,
              width = .4) +
  geom_boxplot(color = "black",
               alpha = .5)+
  theme_gray()+
  ggtitle("Writing vs. Lunch")+
  ggeasy::easy_center_title()
ggsave(here::here("Output", "Figures", "lunch_writing.tiff"), plt3_3_3_3, height = 6, width = 6)
plt3_3_3_3
```


