---
title: "Lab 02 - Plastic waste"
author: "Negar Maleki"
date: "01/28/2022"
output: html_document
---

## Load packages and data

```{r setup, message=FALSE}
# Load the tidyverse package
library(tidyverse)
```

```{r load-data, message=FALSE}
plastic_waste <- read.csv(here::here("data/plastic-waste.csv"))
```

## Exercises

### Exercise 1


```{r plastic-waste-continent}
# 1-1
hist_1 <- ggplot(plastic_waste) +
  aes(x = plastic_waste_per_cap) +
  geom_histogram(binwidth = 1) +
  facet_wrap(~continent)

hist_1 +
  geom_density(aes(y = after_stat(count)))

# 1-2
ggplot(plastic_waste) +
  aes(x = plastic_waste_per_cap, color=continent, fill=continent) +
  geom_density(alpha=0.3)
```


#### 1-3
The color aesthetic typically changes the outside outline of an object and the fill aesthetic is typically the inside shading. However, if we put alpha in aes(), it does not apply the alpha to the legend, so the result doesn't looks good.(we put alpha in the geom to apply it to all attributes of the previous layer)


### Exercise 2

```{r plastic-waste-density}
# insert code here
```

### Exercise 3

Remove this text, and add your answer for Exercise 3 here.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

```{r plastic-waste-violin}
# insert code here
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

```{r plastic-waste-mismanaged}
# insert code here
```

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

```{r plastic-waste-mismanaged-continent}
# insert code here
```

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

```{r plastic-waste-population-total}
# insert code here
```

```{r plastic-waste-population-coastal}
# insert code here
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
# insert code here
```

## Pro-Tips

### Excercise 3

Try this :D

```
ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()+
  geom_boxplot(width=.3, fill="green") +
  stat_summary(fun.y=median, geom="point") 
```

### Exercise 5 

Helpful reference:http://www.sthda.com/english/wiki/ggplot2-themes-and-background-colors-the-3-elements



