---
title: "Lab 02 - Plastic waste"
author: "Negar Maleki"
date: "01/28/2022"
output: html_document
---

## Load packages and data

```{r setup, message=FALSE}
# Load the tidyverse package
library(tidyverse)
```

```{r load-data, message=FALSE}
plastic_waste <- read.csv(here::here("data/plastic-waste.csv"))
```

## Exercises

### Exercise 1

```{r plastic-waste-continent}
# 1-1
hist_1 <- ggplot(plastic_waste) +
  aes(x = plastic_waste_per_cap) +
  geom_histogram(binwidth = 1) +
  facet_wrap(~continent)

hist_1 +
  geom_density(aes(y = after_stat(count)))
```

### Exercise 2

```{r plastic-waste-density}
# insert code here
ggplot(plastic_waste) +
  aes(x = plastic_waste_per_cap, color=continent, fill=continent) +
  geom_density(alpha=0.3)
```

### Exercise 3

When specified inside aes, an aesthetic is mapped to the value of a variable in the data. Since there is a mapping between the data and the visible aesthetic, there is a legend which shows that mapping. Outside of an aes call, the aesthetic is just set to a specific value.

### Exercise 4

```{r plastic-waste boxplot}
p <- ggplot(plastic_waste) +
  aes(x = continent, y = plastic_waste_per_cap, fill=continent) +
  geom_boxplot() 
p
```

### Exercise 5

```{r plastic-waste boxplot+dotplot}
p +
  geom_point()
```

### Exercise 6

```{r plastic-waste raincloud}
p +
  geom_point() +
  ggdist::stat_halfeye(justification = -.2)

```

```{r plastic-waste raincloud2}
t <- ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()+
  geom_boxplot(width=.3, fill="green") +
  stat_summary(fun.y=median, geom="point") 
t
```

### Exercise 7

#### What does the density or data points show that the boxplot does not?

Distribution of other data out of box plot.

### Exercise 8

As we can see in below plot, plastic_waste_per_cap and mismanaged_plastic_waste_per_cap have positive correlation. It means by increasing mismanaged_plastic_waste_per_cap, plastic_waste_per_cap will increase.

```{r plastic-waste-mismanaged}
ggplot(plastic_waste) +
  aes(x = plastic_waste_per_cap, y = mismanaged_plastic_waste_per_cap) +
  geom_point()
```

### Exercise 9

As below plot shows, there does not seem to be any clear distinctions between continents with respect to how plastic waste per capita and mismanaged plastic waste per capita are associated.

```{r plastic-waste-mismanaged-continent}
ggplot(plastic_waste) +
  aes(x = plastic_waste_per_cap, y = mismanaged_plastic_waste_per_cap, color=continent) +
  geom_point(alpha=0.5)
```

### Exercise 10

Remove this text, and add your answer for Exercise 7 here.

```{r plastic-waste-population-total}
ggplot(plastic_waste) +
  aes(x = plastic_waste_per_cap, y = total_pop) +
  geom_point() +
  scale_y_log10(name="log-total pop") +
  geom_smooth()
```

```{r plastic-waste-population-coastal}
ggplot(plastic_waste) +
  aes(x = plastic_waste_per_cap, y = coastal_pop) +
  geom_point() +
  scale_y_log10(name="log-total pop") +
  geom_smooth(method = "lm")
```

#### Do either of these pairs of variables appear to be more strongly associated?

No, they don't.

### Exercise 11

Remove this text, and add your answer for Exercise 11 here.

```{r recreate-viz}
x_axis <- plastic_waste$coastal_pop/plastic_waste$total_pop
plastic_waste$Coastal_population_proportion <- x_axis
ggplot(plastic_waste |>
  filter(plastic_waste_per_cap < 3)) +
  aes(x = Coastal_population_proportion, y = plastic_waste_per_cap) +
  geom_smooth(color='black') +
  geom_point(aes(color=continent)) +
  ggtitle("Plastic waste vs. coastal population proportion
by continent") +
  xlab("Coastal population proportion (Coastal / total population)") + ylab("Plastic waste per capita")
```

## Pro-Tips

### Excercise 3

Try this :D

```
ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()+
  geom_boxplot(width=.3, fill="green") +
  stat_summary(fun.y=median, geom="point") 
```

### Exercise 5 

Helpful reference:http://www.sthda.com/english/wiki/ggplot2-themes-and-background-colors-the-3-elements



