---
title: "Lab-05B"
author: "Negar"
date: "2/22/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
set.seed(123)
missing_w2_parent <- sample(1:500, 30)
missing_w2_child <- c(missing_w2_parent[1:5], sample(1:500, 25))
family  <- read_csv(
  "https://raw.githubusercontent.com/bwiernik/progdata/main/inst/tutorials/data/family_data.csv"
) |> 
  mutate(
    across(
      starts_with("w2") & contains("parent"),
      ~ ifelse(family_id %in% missing_w2_parent, NA_real_, .x)
    ),
    across(
      starts_with("w2") & contains("child"),
      ~ ifelse(family_id %in% missing_w2_child, NA_real_, .x)
    )
  )
```

```{r}
family |> 
  DT::datatable(rownames = FALSE)
```

1. Reshape the dataset to a “longer” format.
- Make each row 1 score
- Have columns for family_id, family_member, wave, scale, and score.

```{r}
family_longest <- family |> 
  pivot_longer(cols = -family_id,  # columns we want to pivot
               names_to = c("wave", "scale", "family_member"),
               names_sep = "_")

print(family_longest)
```

2. Reshape the dataset to a “longer” format.
- Make each row 1 person
- Have columns for family_id, family_member, wave, comm, and satis.

```{r}
family_longest <- family |> 
  pivot_longer(cols = -family_id,  # columns we want to pivot
               names_to = c("wave", ".value", "family_member"),
               names_sep = "_")

print(family_longest)
```

3. Some families are missing wave 2 data for parent, child, or both. Which families are missing wave 2 data for at least one person?

```{r}
apply(is.na(family), 2, which)
```

Question: Is it easier to find the missing data in the wide or long format?

Longer format is much easier to find the missing data.
